Future Directions

### 2015-02-18 slides/bordeaux/slides-1.tex
Working on bordeaux slides

        \vspace{4mm}

@@

                \[
                    p(\divTimeMapVector,
                      \divModel{i},
                      \allParameters{}
                      \given \alignmentVector)
                      =
                    \frac{
                        p(\alignmentVector \given
                          \divTimeMapVector,
                          \allParameters{},
                          \divModel{i})
                        p(\divTimeMapVector,
                          \allParameters{}
                          \given \divModel{i})
                        p(\divModel{i})
                        }{p(\alignmentVector)}
                \]
                \vspace{-1mm}
                \end{minipage}
            \end{displaybox}
        \end{uncoverenv}
    \end{minipage}
\end{frame}

\begin{frame}
    \frametitle{New method: \dppmsbayes}
    \begin{itemize}
        % \item<1-> Reparameterized the model implemented in \msb
        \item<1-> Dirichlet-process prior (DPP) over all possible divergence
            models
        \item<2-> Flexible priors on continuous parameters to avoid strongly
            weighted posteriors
        \item<3-> Multi-processing interface to accommodate genomic datasets
        % \item<4-> Uniform prior over divergence models
    \end{itemize}
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

\begin{frame}
    \frametitle{\dppmsbayes: Performance}
    \begin{itemize}
        \item<1-> Extensive computer simulations to compare performance to previous
            state-of-the-art methods (\msb).
        \item<2-> New method for estimating shared evolutionary history shows
            improved:
            \begin{enumerate}
                \item<2-> Improved model-choice accuracy 
                \item<2-> More robustness to model violations
                \item<2-> Greater power to detect variation in divergence times
                \item<2-> Faster!
            \end{enumerate}
    \end{itemize}

    \uncover<3->{
    \textbf{\dppmsbayes allows biologists to leverage comparative genomic data
        to assess the affects of community-scale processes on biodiversity}
    }
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

        \begin{uncoverenv}<1->
        \colorbox{white}{
            \begin{minipage}[t]{1.0\textwidth}
                \raggedright
                \textbf{Did repeated fragmentation of islands during
                    inter-glacial rises in sea level promote diversification?}
            \end{minipage}
        }
        \end{uncoverenv}
    \end{columns}
\end{frame}
}

@@

\begin{frame}
    \frametitle{Results}
    \centerline{
    \includegraphics[width=\textwidth]{../../empirical-analyses/plots/philippines-dpp-psi-posterior-prior.pdf}}
    \smallskip
    \centerline{
    \includegraphics[height=2cm]{../images/sea-level-only.pdf}}
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

@@

\begin{frame}
    \frametitle{Results}
    \begin{itemize}
        \item<1-> Results consistent with prediction of clustered
            divergences
        \item<2-> Results suggest multiple interglacial periods were important
            drivers of diversification and community assembly across Islands of
            Southeast Asia
        \item<3-> However, there is a lot of uncertainty!
    \end{itemize}
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

>>>>

        % \vspace{1mm}

@@

                \[
                    p(\divTimeMapVector,
                      \divModel{i},
                      \allParameters{}
                      \given \alignmentVector)
                      =
                    \frac{
                        p(\alignmentVector \given
                          \divTimeMapVector,
                          \allParameters{},
                          \divModel{i})
                        p(\divTimeMapVector,
                          \allParameters{}
                          \given \divModel{i})
                        p(\divModel{i})
                        }{p(\alignmentVector)}
                \]
                \vspace{-1mm}
                \end{minipage}
            \end{displaybox}
        \end{uncoverenv}

        \vspace{-1mm}

        \begin{uncoverenv}<4->
            \begin{center}
                \begin{itemize}
                    \small
                    \item Dirichlet-process prior (DPP) over all possible divergence
                        models
                    % \item<2-> Flexible priors on continuous parameters to avoid strongly
                    %     weighted posteriors
                    \item Multi-processing interface to accommodate genomic datasets
                \end{itemize}
            \end{center}
        \end{uncoverenv}
    \end{minipage}
\end{frame}

\begin{frame}
    \frametitle{\dppmsbayes: Performance}
    \begin{itemize}
        \item<1-> Used computer simulations to compare performance to previous
            state-of-the-art methods (\msb).
        \item<2-> New method for estimating shared evolutionary history shows
            improved:
            \begin{enumerate}
                \item<2-> Improved model-choice accuracy 
                \item<2-> More robustness to model violations
                \item<2-> Greater power to detect variation in divergence times
                \item<2-> Faster!
            \end{enumerate}
    \end{itemize}

    % \uncover<3->{
    % \textbf{\dppmsbayes allows biologists to leverage comparative genomic data
    %     to assess the affects of community-scale processes on biodiversity}
    % }
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

{
% \usebackgroundtemplate{\includegraphics[width=\paperwidth]{../images/maps/se-asia-120.png}}
% \begin{frame}
%     % \frametitle{Climate-driven diversification}    
%     \begin{columns}
%         \column{0.6\textwidth}

%         \vspace{6.5cm}

%         \ \\

%         \column{0.4\textwidth}

%         \vspace{-2cm}

%         \begin{uncoverenv}<1->
%         \colorbox{white}{
%             \begin{minipage}[t]{1.0\textwidth}
%                 \raggedright
%                 \textbf{Did repeated fragmentation of islands during
%                     inter-glacial rises in sea level promote diversification?}
%             \end{minipage}
%         }
%         \end{uncoverenv}
%     \end{columns}
% \end{frame}
% }

@@

\begin{frame}
    \frametitle{Results}
    \centerline{
    \includegraphics[height=5cm]{../../empirical-analyses/plots/philippines-dpp-psi-posterior.pdf}}
    \smallskip
    \centerline{
    \includegraphics[height=2cm]{../images/sea-level-only.pdf}}
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

@@

\begin{frame}
    \frametitle{Results}
    \begin{itemize}
        \item \textbf{dpp-msbayes allows biologists to leverage comparative
                genomic data to assess the affects of community-scale processes
                on biodiversity}
        % \item<1-> Results consistent with prediction of clustered
        %     divergences
        \item<2-> Results suggest multiple interglacial periods were important
            drivers of diversification and community assembly across Islands of
            Southeast Asia
        \item<3-> However, there is a lot of uncertainty!
    \end{itemize}
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

### 2015-02-18 slides/bordeaux/slides-2.tex
Working on bordeaux slides

\begin{frame}
    \frametitle{Inferring the evolutionary context of ecosystems}
    \begin{itemize}[<+->]
        \item Use comparative framework to estimate the history of floral and
            faunal communities across Europe
        \item A better understanding of the diversification and assembly
            of communities will provide a framework for understanding
            the affect of past climate change
        \item This will provide context for predicting future change
    \end{itemize}
\end{frame}

\begin{frame}
    \begin{itemize}[<+->]
        \item Generalized birth-death process might better model
            epidemiological dynamics
        \item Could be relevant to the evolution of grapevine pathogens
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Strategies for integration}
    \begin{itemize}[<+->]
        \item In order to predict the response of ecosystems to environmental
            change, we need a general model of ecosystem processes
        \item Organize a series ``hackathons'' to stimulate synthesis among the
            biologists, engineers, and theorists across LabEx 
        \item Each hackathon would focus on integrating processes and existing
            models between particular specialties and/or ecosystems
    \end{itemize}
\end{frame}

>>>>

\begin{frame}
    \frametitle{Relevance to LabEx COTE}
    \begin{itemize}
        \item<2-> Use novel comparative method to estimate the history of floral
            and faunal communities across Europe
        \item<3-> Elucidate the history of communities and their response to past
            environmental climate change
        \item<4-> This will provide context for predicting future change
        \item<5-> Collaboration with BIOGECO partners
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Relevance to LabEx COTE}
    \begin{itemize}[<+->]
        \item Generalized birth-death process will be relevant to
            modeling epidemiological dynamics
        \item Relevant to the evolution of grapevine pathogens
        \item Collaboration with SV partners to investigate disease dynamics
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Strategies for integration}
    \begin{itemize}
        \item<2-> In order to predict the response of ecosystems to environmental
            change, we need a general model of ecosystem processes
        \item<3-> This requires integration across LabEx COTE partners
        \item<3-> Organize a series ``hackathons'' to stimulate synthesis among the
            biologists, engineers, theorists, and modelers across LabEx COTE
        \item<4-> Each hackathon would focus on integrating concepts and existing
            models between particular ecosystems and/or ecosystem processes
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Teaching prospects}
    \begin{itemize}[<+->]
        \item Teach courses at the nexus of evolution, ecology, statistics,
            and computer science
        \begin{itemize}
            \item Computational biology
            \item Advance statistics in biology (likelihood and Bayesian
                approaches)
            \item Advanced methods in evolutionary genetics and
                molecular ecology
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Questions?}    
    \begin{columns}[c]
        \column{.5\textwidth}
        \begin{center}
            {
            \Large
            \href{mailto:joaks1@uw.edu}{\tt joaks1@uw.edu}
            }
        \end{center}
        \column{.5\textwidth}
            \begin{figure}
                \begin{center}
                \includegraphics[width=\textwidth]{../images/darwin-tol-copyright-boris-kulikov-2007.jpg}
                \caption{\tiny \copyright~2007 Boris Kulikov \href{http://boris-kulikov.blogspot.com/}{boris-kulikov.blogspot.com}}
                \end{center}
            \end{figure}
    \end{columns}
\end{frame}
